Summer 2025 ToDo

### 2025-11-12 Relations/Paper/Definitions.tex
paper update
New definition layout. Typos fixed. Proper URLs

% \subsection{Normalization (\texttt{Properties.agda})}
\begin{definition} Let $a \in A$.
  \begin{description}
    \item[\ule{${a \in \NF_R}$}] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
    \item[\ule{$a \in \WN_R$}] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
    \item[\ule{$a \in \SN_R$}] \emph{$a$ is strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = \setof{(y,x) | (x,y) \in R}$.
    See Section \ref{sec:Well-foundedness} for the notion of accessibility.
  \end{description}
\end{definition}

% \subsection{Confluence (\texttt{Properties.agda})}
\begin{definition} Let $a \in A$.
    \begin{description}
        \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser} (or \emph{weakly confluent}) if for all $b,c \in A$, \[c \bstep a \rstep b \implies \exists d.\, c \mstep d \bmstep b\]
        \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser} (or \emph{confluent}) if for all $b,c \in A$, \[c \bmstep a \mstep b \implies \exists d.\, c \mstep d \bmstep b\]
        \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if for all $b, c \in A$,
        \[c \bmstep a \mstep b \implies \exists d. \, c \rrstep d \brstep b\]
        \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if for all $b \in \NF_R$, \[ a \estep b \implies a\mstep b\]
        \item[\ule{$a \in \NP_R$}] \emph{$a$ has the reduction normal form property} if for all $b \in \NF_R$,
        \[c \bmstep a \mstep b \implies c \mstep b\]
        \item[\ule{$a \in \UN_R$}] \emph{$a$ has the conversion unique normal form property} if for all $a, b \in \NF_R$, \[a \estep b \implies a \equiv b\]
        \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the reduction unique normal form property} if for all $b, c \in \NF_R$,
        \[c \bmstep a \mstep b  \implies b \equiv c\]
    \end{description}
\end{definition}
% \begin{definition} Let $a \in A$.
%     \begin{description}
%         \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
%         \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
%         \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
%         \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
%         \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
%         \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
%         \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
%     \end{description}
% \end{definition}

@@

\begin{definition} \label{def:seq} \hfill
  \begin{itemize}
    \item A \emph{sequence} is a function $s$ from the natural numbers to $A$.
    \item A sequence $s : \nat \to A$ is \emph{$R$-decreasing} if every element of the sequence is $R$-related to its preceding term.
    \item A sequence $s : \nat \to A$ is \emph{$R$-increasing} if every element of the sequence is $R$-related to its succeeding term.
  \end{itemize}
\end{definition}

\begin{definition}\hfill
    \begin{description}
        \item[\ule{$x \in CP_R$}] \emph{$x$ has the cofinality property} if there exists an $R^r$-increasing sequence
        \mbox{$s : \nat {\to} A$} starting from $x$ such that every
        reduct of $x$ reduces to some element of the sequence.
        \[ x \mstep y \implies \exists i. y \mstep s(i) \]
        % \item[\ule{$x \in CP_R$}] \emph{$x$ has the cofinality property} if there exists an
        % (not necessarily strictly) increasing sequence starting from $x$ such that every
        % reduct of $x$ reduces to some element of the sequence.
    \end{description}
\end{definition}

\begin{definition} \label{def:bound} \hfill
  \begin{description}
    \item[\ule{$a \in A$ is an $s$-bound}] if for all $i \in \nat$, $s (i) \mstep a$.
    \item[\ule{$s : \nat \to A$ is bounded}] if there exists $a \in A$ that is an $s$-bound.
  \end{description}
\end{definition}

\begin{definition} \label{def:rp}
  The following are global properties of the given relation $R$.  \hfill
    \begin{description}
        \item[\ule{$\gBP(R)$}] \emph{$R$ has the boundedness property} if every $R$-increasing sequence is bounded.
        \item[\ule{$\gRP(R)$}] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that
        $s (i) \mstep x \implies x \mstep s (i)$ for all $x\in A$.
        \item[\ule{$\gRPm(R)$}] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
    \end{description}
\end{definition}

@@

\begin{definition} \hfill
    \begin{description}
        \item[$\gInc(R)$] \emph{$R$ is increasing} if there exists a ``size function'' $|{-}| : A \to \nat$ satisfying, for all $a, b \in A$,
        $(a \rstep b) \implies |a| < |b|$
    \end{description}
\end{definition}

@@

\begin{definition} \hfill
    \begin{description}
        \item[\ule{$a \in \FB$}] \emph{$a$ is finitely branching} if there are finitely many $b \in A$ such that $a \rstep b$.
    \end{description}
\end{definition}

@@

$\FB$ is a property that plays an important role in our discussion of well-foundedness (see Section \ref{sec:Well-foundedness}).

>>>>

% \subsection{Normalization (\texttt{Properties.agda})}
\begin{definition} Let $a \in A$.
  \begin{description}
    \item[\bq \ule{${a \in \NF_R}$}] \emph{$a$ is a normal form} if $(a,b) \notin R$ for any $b \in A$.
    \item[\bq \ule{$a \in \WN_R$}] \emph{$a$ is weakly normalizing} if $a \mstep b$ for some $b \in \NF_R$.
    \item[\bq \ule{$a \in \SN_R$}] \emph{$a$ is strongly normalizing} if $a$ is accessible with respect to the converse relation $\bar{R} = \setof{(y,x) | (x,y) \in R}$.
    See Section \ref{sec:Well-foundedness} for the notion of accessibility.
  \end{description}
\end{definition}

% \subsection{Confluence (\texttt{Properties.agda})}
\begin{definition} Let $a \in A$.
    \begin{description}
        \item[\bq \ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser} (or \emph{weakly confluent}) if for all $b,c \in A$, \[c \bstep a \rstep b \implies \exists d.\, c \mstep d \bmstep b\]
        \item[\bq \ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser} (or \emph{confluent}) if for all $b,c \in A$, \[c \bmstep a \mstep b \implies \exists d.\, c \mstep d \bmstep b\]
        \item[\bq \ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if for all $b, c \in A$,
        \[c \bmstep a \mstep b \implies \exists d. \, c \rrstep d \brstep b\]
        \item[\bq \ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if for all $b \in \NF_R$, \[ a \estep b \implies a\mstep b\]
        \item[\bq \ule{$a \in \NP_R$}] \emph{$a$ has the reduction normal form property} if for all $b \in \NF_R$,
        \[c \bmstep a \mstep b \implies c \mstep b\]
        \item[\bq \ule{$a \in \UN_R$}] \emph{$a$ has the conversion unique normal form property} if for all $a, b \in \NF_R$, \[a \estep b \implies a \equiv b\]
        \item[\bq \ule{$a \in \UNto_R$}] \emph{$a$ has the reduction unique normal form property} if for all $b, c \in \NF_R$,
        \[c \bmstep a \mstep b  \implies b \equiv c\]
    \end{description}
\end{definition}
% \begin{definition} Let $a \in A$.
%     \begin{description}
%         \item[\ule{$a \in \WCR_R$}] \emph{$a$ is weakly Church-Rosser (or weakly confluent)} if $c \bstep a \rstep b \implies c \mstep d \bmstep b$.
%         \item[\ule{$a \in \CR_R$}] \emph{$a$ is Church-Rosser (or confluent)} if $c \bmstep a \mstep b \implies c \mstep d \bmstep b$.
%         \item[\ule{$a \in \CRs_R$}] \emph{$a$ is subcommutative} if $c \bmstep a \mstep b \implies c \rrstep d \brstep b$.
%         \item[\ule{$a \in \NPe_R$}] \emph{$a$ has the conversion normal form property} if $a \estep b \implies a\mstep b$ for any $b \in \NF$.
%         \item[\ule{$a \in \NP_R$}] \emph{$a$ has the normal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \NF$.
%         \item[\ule{$a \in \UN_R$}] \emph{$a$ has the unique normal form property} if $a \estep b \implies a \equiv b$  for any $a, b \in \NF$.
%         \item[\ule{$a \in \UNto_R$}] \emph{$a$ has the unique normal form property with respect to reduction} if $c \bmstep a \mstep b  \implies b \equiv c$  for any $b, c \in \NF$.
%     \end{description}
% \end{definition}

@@

\begin{definition} \label{def:seq} \hfill
  \begin{description}
    \item \bq \ule{A {sequence}} is a function $s$ from the natural numbers to $A$.
    \item \bq \ule{A sequence $s : \nat \to A$ is {$R$-decreasing}} if every element of the sequence is $R$-related to its preceding term.
    \item \bq \ule{A sequence $s : \nat \to A$ is {$R$-increasing}} if every element of the sequence is $R$-related to its succeeding term.
  \end{description}
\end{definition}

\begin{definition}\hfill
    \begin{description}
        \item[\bq \ule{$x \in CP_R$}] \emph{$x$ has the cofinality property} if there exists an $R^r$-increasing sequence
        \mbox{$s : \nat {\to} A$} starting from $x$ such that every
        reduct of $x$ reduces to some element of the sequence.
        \[ x \mstep y \implies \exists i. y \mstep s(i) \]
        % \item[\ule{$x \in CP_R$}] \emph{$x$ has the cofinality property} if there exists an
        % (not necessarily strictly) increasing sequence starting from $x$ such that every
        % reduct of $x$ reduces to some element of the sequence.
    \end{description}
\end{definition}

\begin{definition} \label{def:bound} \hfill
  \begin{description}
    \item[\bq \ule{$a \in A$ is an $s$-bound}] if for all $i \in \nat$, $s (i) \mstep a$.
    \item[\bq \ule{$s : \nat \to A$ is bounded}] if there exists $a \in A$ that is an $s$-bound.
  \end{description}
\end{definition}

\begin{definition} \label{def:rp}
  The following are global properties of the given relation $R$.  \hfill
    \begin{description}
        \item[\bq \ule{$\gBP(R)$}] \emph{$R$ has the boundedness property} if every $R$-increasing sequence is bounded.
        \item[\bq \ule{$\gRP(R)$}] \emph{$R$ has the recurrence property} if for every bounded, increasing sequence $s$ with an $s$-bound, there exists an $i \in \nat$ such that
        $s (i) \mstep x \implies x \mstep s (i)$ for all $x\in A$.
        \item[\bq \ule{$\gRPm(R)$}] \emph{$R$ has the weak recurrence property} if for every increasing sequence $s$ with bound $b$ there exists an $i \in \nat$ such that $b \mstep s (i)$.
    \end{description}
\end{definition}

@@

\begin{definition} \hfill
    \begin{description}
        \item[\bq  \ule{$\gInc(R)$}] \emph{$R$ is increasing} if there exists a ``size function'' $|{-}| : A \to \nat$ satisfying, for all $a, b \in A$,
        $(a \rstep b) \implies |a| < |b|$
    \end{description}
\end{definition}

@@

\begin{definition} \hfill
    \begin{description}
        \item[\bq \ule{$a \in \FB$}] \emph{$a$ is finitely branching} if there are finitely many $b \in A$ such that $a \rstep b$.
    \end{description}
\end{definition}

@@

$\FB$ plays an important role in our discussion of well-foundedness, see Section \ref{sec:Well-foundedness}.

### 2025-11-12 Relations/Paper/Implications.tex
New definition layout. Typos fixed. Proper URLs

\begin{definition}\label{def:mf} Let $a \in A$. \hfill
    \begin{description}
        \item[\ule{$a \in \MF_R$}] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
        \item[\ule{$a \in \WM_R$}] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
        \item[\ule{$a \in \SM_R$}]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is strongly minimalizing. (This
        definition is to be understood inductively).
        \item[\ule{$a \in \SMseq_R$}] \emph{$a$ is sequentially strongly minimalizing} if for every $R$-increasing sequence $s$ starting at $a$, there exists
        an $i \in \nat$ such that $s (i) \in \MF$.
        \item[\ule{$a \in \MP_R$}] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
    \end{description}
\end{definition}

@@

In contrast to the above proposition, the inclusion $\SN \subset \SM \cap \WN $ is strict: in Counterexample~\ref{CE:4}, $a \in \SM \cap \WN$, but $a \notin \SN$. In the tables below, we therefore include a seperate column for the combination of $\SM$ and $\WN$.

>>>>

\begin{definition}\label{def:mf} Let $a \in A$. \hfill
    \begin{description}
        \item[\bq \ule{$a \in \MF_R$}] \emph{$a$ is a minimal form} if $a \mstep b \implies b \mstep a$ for any $b \in A$.
        \item[\bq \ule{$a \in \WM_R$}] \emph{$a$ is weakly minimalizing} if $a \mstep b$ for some $b \in \MF_R$.
        \item[\bq \ule{$a \in \SM_R$}]  \emph{$a$ is strongly minimalizing} if either $a \in MF_R$, or every element one $R$ step from $a$ is strongly minimalizing. (This
        definition is to be understood inductively).
        \item[\bq \ule{$a \in \SMseq_R$}] \emph{$a$ is sequentially strongly minimalizing} if for every $R$-increasing sequence $s$ starting at $a$, there exists
        an $i \in \nat$ such that $s (i) \in \MF$.
        \item[\bq \ule{$a \in \MP_R$}] \emph{$a$ has the minimal form property} if $c \bmstep a \mstep b \implies c \mstep b$ for any $b \in \MF$.
    \end{description}
\end{definition}

@@

In contrast to the above proposition, the inclusion $\SN \subset \SM \cap \WN $ is strict: in Counterexample~\ref{CE:4}, $a \in \SM \cap \WN$, but $a \notin \SN$. In the tables below, we therefore include a separate column for the combination of $\SM$ and $\WN$.
